---
title: "Deskriptive Statistik und Regressionen"
author: "Lena Ziegler und Alexandra Grau"
date: "10/9/2019"
output: 
  html_document: 
    fig_caption: yes
    toc: yes
    number_sections: false
    toc_depth: 4
    fig.retina: 4
    fig.caption: true
    fig.width: 12
    fig.height: 4
    code_folding: show
    df_print: paged
    toc_float: 
      collapsed:  false
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

## Libraries

```{r}
library(tidyverse)
library(scales)
library(leaps)
library(MASS)
library(caret)
library(ridge)
library(randomForest)
library(caTools)
library(e1071)
library(glmnet)
library(pROC)
library(ggplot2)
library(sjPlot)
library(tadaatoolbox)
library(broom)
options(scipen = 999)

```


## Read data file

```{r}
ts_new_york_tbl <- read_csv("ts_new_york.csv") %>%
 dplyr::select(-1, -2, -3, -6, -13, -14, -15,-16)
```


#shows the entire data set
```{r}
ts_new_york_tbl
```


#shows the first 7 rows
```{r}
head(ts_new_york_tbl)
```


#shows the last 7 rows
```{r}
tail(ts_new_york_tbl)
```


#shows the variable names and types
```{r}
str(ts_new_york_tbl)
```

## Some Visualizations

### Exploring the boroughs contained in the data set

```{r}
ts_new_york_tbl %>% 
  filter(!borough == "NA") %>% 
  group_by(borough) %>% 
  summarise(Count = n()) %>% 
  ggplot(mapping = aes(x = reorder(borough, Count), y = Count, fill = borough)) +
  geom_col(width = 0.6, show.legend = FALSE) +
  labs(title = "Boroughs of New York",
       subtitle = "AirBnBs per Borough",
       x = "Boroughs", y = "Count") +
  theme_tadaa()
```

### Exploring the room types

```{r}
ts_new_york_tbl %>% 
  filter(!room_type == "NA") %>% 
  group_by(room_type) %>% 
  summarise(Freq = n()) %>% 
mutate(prop = Freq/sum(Freq)) %>% 
  filter(Freq != 0) %>% 
  
  ggplot(mapping = aes(x = 2, y = prop, fill = room_type))+
  geom_bar(width = 1, color = "white", stat = "identity") +
  xlim(0.5, 2.5) +
  coord_polar(theta = "y", start = 0) +
  theme_void() +
  scale_y_continuous(labels = percent) +
  geom_text(aes(label = paste0(round(prop*100, 1), "%")), size = 3.5, position = position_stack(vjust = 0.5)) +
  scale_fill_brewer(palette = "Blues", direction = 1) +
  #theme(axis.text.x = element_text(angle = 90), legend.position = "top")+
  labs(title = "Room types",
       x = "",
       y = "",
       fill = "Key") +
  theme(legend.position = "right")
```

### Exploring price and satisfaction
```{r}
ggplot(data = ts_new_york_tbl, aes(x = price, y = overall_satisfaction, color = room_type)) +
  geom_point() +
  scale_color_brewer(palette = "Set2") +
  ggtitle(" Price and Overall Satisfaction") +
  xlab("Price") +
  ylab("Overall Satisfaction")
```

### Average Rent in different Borough for different apartment types

```{r}
ts_new_york_tbl %>%
  filter(!room_type == "NA") %>% 
  group_by(room_type, borough) %>% 
  summarise(avePrice = mean(price, na.rm = TRUE)) %>% 
  ggplot(mapping = aes(x = reorder(borough, avePrice), y = avePrice, fill = room_type)) +
  geom_col(width = 0.6, show.legend = FALSE) +
  facet_wrap(. ~ room_type, scales = "free_y") +
  labs(x = "Borough",
       y = "Average Price") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90, vjust = 1.1, hjust = 1.0))
```


### Exploring the distribution of the price variable

```{r}
ts_new_york_tbl %>% 
  filter(!price == "NA") %>% 
  ggplot(mapping = aes(x = price)) +
  geom_histogram(fill = "#DA9112", bins = 50, stat = "density", alpha = 0.6) +
  labs(x = "Price",
       y = "Count")+
  theme_bw()+
    scale_x_continuous(labels = scales::comma)
```

### Exploring the relationship between reviews score and price

```{r}

ts_new_york_tbl %>% 
  filter(!reviews == "NA", !price == "NA") %>% 
  ggplot(mapping = aes(x = reviews, y = price)) +
  geom_point(color = "steelblue") +
  labs(x = "Reviews",
       y = "Price")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 0)) +
    scale_y_continuous(labels = scales::comma)

```


### Exploring the relationship among the variables

```{r}
ts_new_york_tbl %>% 
  dplyr::select(-room_type, -borough) %>% 
  cor(., use = "pairwise.complete.obs") %>% 
  ggcorrplot::ggcorrplot(., method = "square", type = "lower",hc.order = TRUE,outline.color = "white",ggtheme = ggplot2::theme_gray(),lab = TRUE)
```

### Have a look at Price and Overall Satisfaction
```{r}
ggplot(ts_new_york_tbl, aes(x=price, y=overall_satisfaction)) +
  geom_smooth(method ="lm") +
  coord_cartesian() +
  scale_color_gradient() +
  theme_bw() +
  ggtitle(" Price and Overall Satisfaction") +
  xlab("Price") +
  ylab("Overall Satisfaction")
```

### Have a look at Price and Bedrooms
```{r}
ggplot(ts_new_york_tbl, aes(x=price, y=bedrooms)) +
  geom_smooth(method ="lm") +
  coord_cartesian() +
  scale_color_gradient() +
  theme_bw() +
  ggtitle(" Price and Bedrooms") +
  xlab("Price") +
  ylab("Bedrooms")
```



## Exploring different linear models
### Linear regression

```{r}
ts_new_york_tbl <- ts_new_york_tbl
model1 <- lm(price ~ ., data = ts_new_york_tbl, na.action = "na.omit")
tab_model(model1)
summary(model1)
```


#### Plotting variable importance for the linear model object

```{r}
varImptest <- varImp(model1)
variables <- row.names(varImptest)
effect <- varImptest$Overall

varImp_tbl <- bind_cols(variables = variables, effect = effect)

varImp_tbl %>% 
  ggplot(mapping = aes(x = reorder(variables, effect), y = effect)) +
  geom_col(width = 0.6, fill = "steelblue") +
  coord_flip() +
  theme_bw() +
  labs(x = "Explanatory variables",
       y = "Effect size")

```


### Stepwise Linear Regression

```{r}
model1 <- lm(price ~ ., data = ts_new_york_tbl, na.action = "na.omit")
stepModel <- step(model1)
summary(stepModel)
tab_model(stepModel)
```


#### Plotting variable importance for the stepwise linear model object

```{r}
varImptest <- varImp(stepModel)
variables <- row.names(varImptest)
effect <- varImptest$Overall

varImp_tbl <- bind_cols(variables = variables, effect = effect)

varImp_tbl %>% 
  ggplot(mapping = aes(x = reorder(variables, effect), y = effect)) +
  geom_col(width = 0.6, fill = "#C9146C") +
  coord_flip() +
  theme_bw() +
  labs(x = "Explanatory variables",
       y = "Effect size")

```

### Split into Train and Validation sets
## Training Set : Validation Set = 70 : 30 (random)
```{r}
set.seed(100)
train <- sample(nrow(ts_new_york_tbl), 0.7*nrow(ts_new_york_tbl), replace = FALSE)
TrainSet <- ts_new_york_tbl[train,]
ValidSet <- ts_new_york_tbl[-train,]
summary(TrainSet)
summary(ValidSet)
```

### Create a Ridge Regression with splitted data
```{r fig.width=10, fig.height=7}

model3 <- linearRidge(price ~ ., data = TrainSet, importance = TRUE) 
model3

```


### Support Vector Machine (SVM) | Radial Kernel

```{r}

model5 <- svm(price ~ ., data = TrainSet, na.action = na.omit, kernel = "radial")

model5

```


### Support Vector Machine (SVM) | Polynomial Kernel

```{r}

model6 <- svm(price ~ ., data = TrainSet, na.action = na.omit, kernel = "polynomial", degree = 4)

model6

```

### Random Forest


```{r}
model10 <- randomForest(price ~ ., data = dplyr::select(TrainSet, 
                                                       -room_type, -borough), 
                       na.action = na.omit, ntree = 500, mtry = 5, importance = TRUE)
model10
```

```{r}
# Predicting on train set
predTrain <- predict(model10, TrainSet, type = "class")
# Checking classification accuracy
table(predTrain, TrainSet$price)  
```


```{r}
# Predicting on Validation set
predValid <- predict(model10, ValidSet, type = "class")
# Checking classification accuracy
mean(predValid == ValidSet$price)                    
table(predValid,ValidSet$price)
```


```{r}
# To check important variables
importance(model10)        
varImpPlot(model10)   
```

                       

```{r}
# Using For loop to identify the right mtry for model
a=c()
i=5
for (i in 3:8) {
  model11 <- randomForest(price ~ ., data = dplyr::select(TrainSet, 
                                                       -room_type, -borough), 
                       na.action = na.omit, ntree = 500, mtry = 6, importance = TRUE, ylim=c(0,300))
  predValid <- predict(model11, ValidSet, type = "class")
  a[i-2] = mean(predValid == ValidSet$price)
}
 
a

plot(model11)

```



